### 2016-02-01 ch05-initvals/InitialValuesPaper.tex
Table with success rates for stress test
Using tolerance 0.02.

\subsection{Stress test of the smoothers}
To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
In particular, we used
\begin{itemize}
  \item low-pass, high-pass, band-pass and band-stop 
  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
\end{itemize}
discrete-time filters (see \figref{fig:bodeplots}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} and an SNR of $20 \unit{dB}$ and $N=1024$ measured samples.
The band-pass and band-stop filters actually have a model order of 20.

\TODO{add table with different transfer functions, generation code, etc. for stress test}

@@

\begin{table}[p]
  \centering
% \input{\thisDir/table2.tex}
  \caption{Overview of the test cases for the initialization stress test.}
\begin{tabular}{crlrrrr}
\toprule
\textsc{Case}   &  \multicolumn{2}{c}{\textsc{Filter}}   &  $\true{\eta}$  &  $\eta_{\mathrm{exist}}$   &  $\eta_{\mathrm{RFIR}}$  &  $\eta_{\mathrm{best}}$ \\
\midrule
1  &  {Chebyshev I}  &  low-pass   &  0  &  0  &  0  &  0\\
2  &  {Chebyshev I}  &  band-pass   &  0  &  0  &  0  &  0\\
3  &  {Chebyshev I}  &  high-pass   &  0  &  0  &  0  &  0\\
4  &  {Chebyshev I}  &  band-stop   &  0  &  0  &  0  &  0\\
5  &  {Chebyshev II}   &  low-pass   &  0  &  0  &  0  &  0\\
6  &  {Chebyshev II}   &  band-pass   &  0  &  0  &  0  &  0\\
7  &  {Chebyshev II}   &  high-pass   &  0  &  0  &  0  &  0\\
8  &  {Chebyshev II}   &  band-stop   &  0  &  0  &  0  &  0\\
9  &  Elliptical   &  low-pass   &  0  &  0  &  0  &  0\\
10   &  Elliptical   &  band-pass   &  0  &  0  &  0  &  0\\
11   &  Elliptical   &  high-pass   &  0  &  0  &  0  &  0\\
12   &  Elliptical   &  band-stop   &  0  &  0  &  0  &  0\\
13   &  Butterworth  &  low-pass   &  0  &  0  &  0  &  0\\
14   &  Butterworth  &  band-pass   &  0  &  0  &  0  &  0\\
15   &  Butterworth  &  high-pass   &  0  &  0  &  0  &  0\\
16   &  Butterworth  &  band-stop   &  0  &  0  &  0  &  0\\
\bottomrule
\end{tabular}
\label{tbl:init:stresstest}
\end{table}

\subsection{Observations}
The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.

>>>>

\subsection{Stress test of the smoothers}
To test the effectiveness of the initial estimates obtained from these particular smoothers, an extra set of $n_{\mathrm{MC}} = 100$ Monte Carlo simulations were performed.
In particular, all combinations of
\begin{itemize}
  \item low-pass, high-pass, band-pass and band-stop 
  \item Chebyshev Type I, Chebyshev Type II, Elliptical and Butterworth
\end{itemize}
discrete-time filters (see \figref{fig:bodeplots} and \tabref{tbl:init:stresstest}) of tenth degree generated by the MATLAB functions \texttt{cheby1}, \texttt{cheby2}, \texttt{ellip} and \texttt{butter} and an SNR of $20 \unit{dB}$ and $N=1024$ measured samples.
All filters $G$ have been normalized in such a way that $\norm[2]{G} = 1$.
The low-pass and high-pass filtes have a cross-over frequency of $\frac{\pi}{2} \unit{rad/S}$. 
The band-pass, respectively band-stop, filters have a passband, respectively stopband, in the frequency range$\left[ \frac{2\pi}{5}, \frac{3\pi}{5}\right] \unit{rad/S}$.
Note also that both the band-pass and band-stop filters have a McMillan degree of 20 as per the \MATLAB conventions.

@@

\begin{table}[p]
  \centering
% \input{\thisDir/table2.tex}
  \caption{Overview of the test cases for the initialization stress test.}
\begin{tabular}{crlrrrrr}
\toprule
\textsc{Case}   &  \multicolumn{2}{c}{\textsc{Filter}}   &  $\true{\eta} [\%]$  &  $\eta_{\mathrm{exist}} [\%]$ &  $\eta_{\mathrm{trunc}} [\%]$   &  $\eta_{\mathrm{RFIR}} [\%]$  &  $\eta_{\mathrm{best}} [\%]$ \\
\midrule
1  &  {Chebyshev I}  &  low-pass   & 100 & 100 & 95  & 100 & 100\\
2  &  {Chebyshev I}  &  band-pass   & 100 & 14  & 7 & 16  & 34\\
3  &  {Chebyshev I}  &  high-pass     & 100 & 100 & 96  & 100 & 100\\
4  &  {Chebyshev I}  &  band-stop     & 100 & 40  & 28  & 74  & 90\\
5  &  {Chebyshev II}   &  low-pass     & 100 & 98  & 73  & 100 & 100\\
6  &  {Chebyshev II}   &  band-pass     & 100 & 23  & 16  & 70  & 79\\
7  &  {Chebyshev II}   &  high-pass     & 100 & 97  & 74  & 100 & 100\\
8  &  {Chebyshev II}   &  band-stop     & 16  & 0 & 0 & 0 & 0\\
9  &  Elliptical   &  low-pass     & 100 & 83  & 34  & 95  & 98\\
10   &  Elliptical   &  band-pass     & 100 & 0 & 0 & 2 & 1\\
11   &  Elliptical   &  high-pass     & 100 & 83  & 33  & 97  & 100\\
12   &  Elliptical   &  band-stop     & 0 & 0 & 0 & 0 & 0\\
13   &  Butterworth  &  low-pass     & 100 & 100 & 100 & 100 & 100\\
14   &  Butterworth  &  band-pass     & 100 & 100 & 100 & 100 & 100\\
15   &  Butterworth  &  high-pass     & 100 & 100 & 100 & 100 & 100\\
16   &  Butterworth  &  band-stop     & 100 & 100 & 100 & 100 & 100\\
\bottomrule
\end{tabular}
\label{tbl:init:stresstest}
\end{table}

\subsection{Observations}
The transfer functions are shown in \figref{fig:bodeplots} while the empirical cumulative validation distance is shown in \figref{fig:distancesStress}.
In \tabref{tbl:init:stresstest}, also the success rates per method are given when a tolerance $tol = 0.02$ is used.
